\scshape Advanced game theory

### 2025-09-30 ms.tex
Add files via upload

Given non-empty sets $X$, $Y$ and $Z$ and functions $f : X \to Y$ and $g : Y \to Z$, the \emph{composition} of $f$ and $g$ is the function $f \circ g : X \to Z$ defined by $(f \circ g)(x) \coloneqq f(g(x))$ for each $x \in X$. Given non-empty sets $X$, $Y$ and $Z$ such that $X \supseteq Y$ and a function $f : X \to Z$, the \emph{restriction of $f$ to $Y$,} often denoted by `$f|_Y$', is the function $g : Y \to Z$ defined by $g(y) \coloneqq f(y)$ for every $y \in Y$.

>>>>

Given non-empty sets $X$, $Y$ and $Z$ and functions $f : X \to Y$ and $g : Y \to Z$, the \emph{composition} of $f$ and $g$ is the function $g \circ f : X \to Z$ defined by $(g \circ f)(x) \coloneqq g(f(x))$ for each $x \in X$. Given non-empty sets $X$, $Y$ and $Z$ such that $X \supseteq Y$ and a function $f : X \to Z$, the \emph{restriction of $f$ to $Y$,} often denoted by `$f|_Y$', is the function $g : Y \to Z$ defined by $g(y) \coloneqq f(y)$ for every $y \in Y$.
